EGGs are adhesive!

### 2025-05-19 calco/final.tex
typo

\begin{center}\begin{tikzpicture}[baseline=(w)]
        \begin{pgfonlayer}{nodelayer}
                \node[style=small box](a) at (-1.8, 0){$a$};
                \node[style=none] (aatt) at (-1.5, 0){};
                \node[style=node](v) at (-0.9, 0){};
                \node[style=medium box](div) at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, -0.3){};
                \node[style=none] (divsnd) at (-0.3, 0.3){};
                \node[style=none] (divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
                \draw(aatt.center) to (v);
                \draw[out=-60, in=-180] (v) to (divfst.center);
                \draw[out=60, in=-180](v) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
\end{tikzpicture}
\qquad
\begin{tikzpicture}[baseline=(w)]
        \begin{pgfonlayer}{nodelayer}
                \node[style=small box](a1) at (-1.8, -0.5){$a$};
                \node[style=none] (a1att) at (-1.5, -0.5){};
                \node[style=node](v1) at (-0.9, -0.5){};
                \node[style=small box](a2) at (-1.8, 0.5){$a$};
                \node[style=none] (a2att) at (-1.5, 0.5){};
                \node[style=node](v2) at (-0.9, 0.5){};
                \node[style=medium box](div) at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, -0.3){};
                \node[style=none] (divsnd) at (-0.3, 0.3){};
                \node[style=none] (divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
                \draw(a1att.center) to (v1);
                \draw(a2att.center) to (v2);
                \draw[out=0, in=-120] (v1) to (divfst.center);
                \draw[out=0, in=120](v2) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
        \begin{pgfonlayer}{eqlayer}
                \draw[dashed, rounded corners] (-1.2, -0.8) rectangle (-0.6, 0.8);
        \end{pgfonlayer}
\end{tikzpicture}
\qquad
\begin{tikzpicture}[baseline=(w)]
        \begin{pgfonlayer}{nodelayer}
                \node[style=small box](a1) at (-1.8, -0.5){$a$};
                \node[style=none] (a1att) at (-1.5, -0.5){};
                \node[style=node](v1) at (-0.9, -0.5){};
                \node[style=small box](a2) at (-1.8, 0.5){$a$};
                \node[style=none] (a2att) at (-1.5, 0.5){};
                \node[style=node](v2) at (-0.9, 0.5){};
                \node[style=medium box](div) at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, -0.3){};
                \node[style=none] (divsnd) at (-0.3, 0.3){};
                \node[style=none] (divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
                \draw(a1att.center) to (v1);
                \draw(a2att.center) to (v2);
                \draw[out=0, in=-120] (v1) to (divfst.center);
                \draw[out=0, in=120](v2) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
\end{tikzpicture}
\end{center}
%
The left-most and the right-most images represent just ordinary term graphs, the middle one is a term graph with equivalence.
As such, they are all objects of $\EqTGs$.
However, note that the right-most image is not an object of $\eg$:
%$\GEqTGs$: 
constants have no input, 
and nodes that are targets of edges with the same label and whose source is the empty word must be equivalent
and possibly coincide,
as in the middle and in the left-most image, respectively,

@@

\bibliography{biblio}

\appendix

>>>>

\begin{center}\begin{tikzpicture}[baseline=(w)]
        \begin{pgfonlayer}{nodelayer}
                \node[style=small box](a) at (-1.8, 0){$a$};
                \node[style=none] (aatt) at (-1.5, 0){};
                \node[style=node](v) at (-0.9, 0){};
                \node[style=medium box](div) at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, -0.3){};
                \node[style=none] (divsnd) at (-0.3, 0.3){};
                \node[style=none] (divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
                \draw(aatt.center) to (v);
                \draw[out=-60, in=-180] (v) to (divfst.center);
                \draw[out=60, in=-180](v) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
\end{tikzpicture}
\qquad
\begin{tikzpicture}[baseline=(w)]
        \begin{pgfonlayer}{nodelayer}
                \node[style=small box](a1) at (-1.8, -0.5){$a$};
                \node[style=none] (a1att) at (-1.5, -0.5){};
                \node[style=node](v1) at (-0.9, -0.5){};
                \node[style=small box](a2) at (-1.8, 0.5){$a$};
                \node[style=none] (a2att) at (-1.5, 0.5){};
                \node[style=node](v2) at (-0.9, 0.5){};
                \node[style=medium box](div) at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, -0.3){};
                \node[style=none] (divsnd) at (-0.3, 0.3){};
                \node[style=none] (divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
                \draw(a1att.center) to (v1);
                \draw(a2att.center) to (v2);
                \draw[out=0, in=-120] (v1) to (divfst.center);
                \draw[out=0, in=120](v2) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
        \begin{pgfonlayer}{eqlayer}
                \draw[dashed, rounded corners] (-1.2, -0.8) rectangle (-0.6, 0.8);
        \end{pgfonlayer}
\end{tikzpicture}
\qquad
\begin{tikzpicture}[baseline=(w)]
        \begin{pgfonlayer}{nodelayer}
                \node[style=small box](a1) at (-1.8, -0.5){$a$};
                \node[style=none] (a1att) at (-1.5, -0.5){};
                \node[style=node](v1) at (-0.9, -0.5){};
                \node[style=small box](a2) at (-1.8, 0.5){$a$};
                \node[style=none] (a2att) at (-1.5, 0.5){};
                \node[style=node](v2) at (-0.9, 0.5){};
                \node[style=medium box](div) at (0, 0){$/$};
                \node[style=none](divfst) at (-0.3, -0.3){};
                \node[style=none] (divsnd) at (-0.3, 0.3){};
                \node[style=none] (divout) at (0.3, 0){};
                \node[style=node] (w) at (0.9, 0){};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
                \draw(a1att.center) to (v1);
                \draw(a2att.center) to (v2);
                \draw[out=0, in=-120] (v1) to (divfst.center);
                \draw[out=0, in=120](v2) to (divsnd.center);
                \draw(divout.center) to (w);
        \end{pgfonlayer}
\end{tikzpicture}
\end{center}
%
The left-most and the right-most images represent just ordinary term graphs, the middle one is a term graph with equivalence.
As such, they are all objects of $\EqTGs$.
However, note that the right-most image is not an object of $\eg$:
%$\GEqTGs$: 
constants have no input, 
and nodes that are targets of edges with the same label and whose source is the empty word must be equivalent
and possibly coincide,
as in the middle and in the left-most image, respectively.

@@

\newpage
\bibliography{biblio}

\newpage
\appendix
